---
title: "HWK2_Data607_F20"
author: "LeTicia Cancel"
date: "9/5/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is an analysis of movie reviews taken from five imaginary individuals. Each “reviewer” was asked to share their opinion of up to six films on a scale of 1 – 5 with 1 being “Below Average” and 5 being “Excellent”. There is also a response of N/A – Did not watch film which is meant to catch any reviewers who left the question blank. 

Packages needed
```{r warning=FALSE, message=FALSE}
#install.packages("RPostgres")
library(DBI)
library(RCurl)
library(ggplot2)
```

## Connect to Database

I created a database using PostgreSQL with 3 tables. One to hold all responses, one with reviewer information, and the third with just the movie names. 

Connect to PostgreSQL DB by replacing all variables with your own credientials.
```{r}
dbName <- 'data607'
host <- 'localhost'
port <- 5432
user <- 'postgres'
password <- 'xxx'

# Create connection and save it to con
con <- dbConnect(RPostgres::Postgres(), dbname = dbName,
                 host = host,
                 port = port, 
                 user = user, 
                 password = password)
```

## Database Setup

You will need to create 3 tables using csv data saved in GitHub.
```{r}
#Movies data
x1 <- getURL("https://raw.githubusercontent.com/ltcancel/HWK2_Data607_F20/master/movies.csv")

df1 <- read.csv(text = x1)

#Reviewers
x2 <- getURL("https://raw.githubusercontent.com/ltcancel/HWK2_Data607_F20/master/reviewers.csv")

df2 <- read.csv(text = x2)

#Review results
x3 <- getURL("https://raw.githubusercontent.com/ltcancel/HWK2_Data607_F20/master/Movie%20Review%20Results.csv")

df3 <- read.csv(text = x3)


```


Create the tables and load the information at the same time using dbWriteTable(). Then use dbListTables(con) to verify that the tables were created. You should have a table called movies, reviewers, and results. 
```{r}

dbWriteTable(con, "movies", df1, row.names = FALSE)
#dbReadTable(con, "movies")

#rename weird column name


dbWriteTable(con, "reviewers", df2, row.names = FALSE)
#dbReadTable(con, "reviewers")

dbWriteTable(con, "results", df3, row.names = FALSE)
#dbReadTable(con, "results")

dbListTables(con)
```

Query the data needed for your analysis. Since the main results table only has the reviewer’s ID we will join with the reviewers table to get the reviewer’s name. 
```{r}

res <- dbGetQuery(con, 'SELECT b."last_name", b."first_name",
           a."Movie_Desc", a."Opinion_Desc" 
           FROM results a
           INNER JOIN reviewers b ON a."Respondent" = b."X.U.FEFF.reviewer_id"')

#preview results of query
head(res)
```


## Analysis

I used ggplot to create a barplot showing the ratings for each movie. I flipped the table, so the x-axis is on the left because some of the ratings name are long and get bunched up making it difficult to read. I kept the N/A data for this table because I thought it was important to know which movie had the least number of views out of all the reviewers. Parasite had the most N/A responses and Frozen II is not part of this bar at all, so I know that each reviewer has seen this film. 
```{r}
ggplot(data = res) +
  geom_bar(
    mapping = aes(x = Opinion_Desc, fill = Movie_Desc), position = "fill"
  ) +
  coord_flip() +
  labs(x = "Rating", title = "Movie Ratings", fill = "Movie Titles")
```

Analyze data without the N/A responses
```{r}
res2 <- dbGetQuery(con, 'SELECT b."last_name", b."first_name",
           a."Movie_Desc", a."Opinion_Desc" 
           FROM results a
           INNER JOIN reviewers b ON a."Respondent" = b."X.U.FEFF.reviewer_id"
           WHERE a."Opinion_Cd" != 5')

head(res2)

ggplot(data = res2) +
  geom_bar(
    mapping = aes(x = Opinion_Desc, fill = Movie_Desc), position = "fill"
  ) +
  coord_polar() +
    labs(x = "Rating", title = "Movie Ratings", fill = "Movie Titles")
```

Conclusion 


Disconnect from db
```{r}
dbDisconnect(con)
```

